Universal Anonymous Signatures

### 2022-08-19 prism-backend/research/gsac/app-related-proofs.tex
Refined model for RAC. Conclusion. Complete draft (excl. app. D)

We prove that \CUASAC is an anonymous and unforgeable anonymous credential
scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
is anonymous and unforgeable. Note that AC schemes modelled as in \cite{fhs19}
do not have issuance anonymity, as the user public key is passed to the issuer.

\begin{theorem}[Anonymity of \CUASAC]
  \label{thm:anon-cuasac}
  If the base \CUASGen construction is anonymous according to
  \defref{def:anonymity-uas}, then \CUASAC is an anonymous AC scheme according
  to \cite{fhs19}.
\end{theorem}

\begin{proof}
  Given \adv~against anonymity of \CUASAC as defined in \cite{fhs19}, we build
  an adversary \advB against anonymity of \CUASGen as defined in
  \defref{def:sign-anonymity-uas}.

  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR$, \advB redirects to
  \HUGEN,\CUGEN,\OBTAIN,\SIGN,\CHALb, respectively. Note that ``translating''
  the inputs from the former into inputs for the latter is trivial.
  Obviously, if \adv~wins in its anonymity game, then so does \advB with the
  same probability.
  % 
  \qed
\end{proof}

@@

We prove that \CUASRAC is an anonymous and unforgeable anonymous credential
scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
has signature anonymity and is unforgeable.

\begin{theorem}[Anonymity of \CUASRAC]
  \label{thm:anon-cuasrac}
  If the base \CUASGen construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, and $F$ is one-way, then \CUASAC is an
  anonymous AC scheme according to \cite{fhs19}.
\end{theorem}

\begin{proof}
  Given \adv~ against anonymity of \CUASRAC as defined in
  \figref{fig:model-rac}, we build an adversary \advB against anonymity of
  \CUASGen as defined in \defref{def:sign-anonymity-uas}.

  First observe that, given a revocation handles $F(V,\cidi)$ and $F(V,\cidu)$
  extracted from any credential showing, it is not possible to extract $\cidi$
  nor $\cidu$, as $F$ is one-way.

  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR,ReqCredHandle$, \advB
  redirects to \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, or \OPEN, respectively.
  Note that ``translating'' the inputs from the former into inputs for the
  latter is trivial. Also, observe that $ReqCredHandle$/\OPEN essentially
  refuses to open transcripts from challenge users (signatures, in the
  non-interactive equivalent), as $F(V,\ccidi_0) \neq F(V,\ccidi_1)$ (and,
  similarly, for $\ccidu_b$) with overwhelming probability (see the $\tyinsp
  \neq \yinsp$) check in \figref{fig:oracles2}. Obviously, if \adv~wins in its
  anonymity game, then so does \advB with the same probability.
  % 
  \qed
\end{proof}

@@

  To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
  that \adv~wins its game via the winning condition of line 7 in the RAC
  unforgeability game. The same reasoning as in \CUASAC applies here. Next, note
  that the probability of \adv~winning its game via the winning condition at
  line 9 is negligible, due to soundness of the NIZK scheme used for signing,
  and the one-wayness of $F$ in $\feval^{\dattrs,F,V,L}$ and $\finsp^{F}$.
  % 
  \qed
\end{proof}

>>>>

We prove that \CUASAC is an anonymous and unforgeable anonymous credential
scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
is anonymous and unforgeable. Note that AC schemes modelled as in \cite{fhs19}
do not have issuance anonymity, as the user public key is passed to the issuer.
Note that, for ease of reference to the games in \secref{sec:formal-uas}, we
reduce to security of \CUASGen rather than to $\CUASGen^{int}$. The
``translation'' between \CUASGen and $\CUASGen^{int}$ is trivial, though.

\begin{theorem}[Anonymity of \CUASAC]
  \label{thm:anon-cuasac}
  If the base \CUASGen construction is anonymous according to
  \defref{def:sign-anonymity-uas}, then \CUASAC is an anonymous AC scheme
  according to \cite{fhs19}.
\end{theorem}

\begin{proof}
  Given \adv~against anonymity of \CUASAC as defined in \cite{fhs19}, we build
  an adversary \advB against signature anonymity of \CUASGen as defined
  in \defref{def:sign-anonymity-uas}.

  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR$, \advB redirects to
  \HUGEN,\CUGEN,\OBTAIN,\SIGN,\CHALb, respectively. Note that translating
  the inputs from the former into inputs for the latter is trivial.
  Obviously, if \adv~wins in its anonymity game, then so does \advB with the
  same probability.
  % 
  \qed
\end{proof}

@@

We prove that \CUASRAC is an anonymous and unforgeable anonymous credential
scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
has signature anonymity and is unforgeable.
%
As for \CUASAC, we reduce to security of \CUASGen rather than to
$\CUASGen^{int}$. The ``translation'' between \CUASGen and $\CUASGen^{int}$ is
again trivial.

\begin{theorem}[Anonymity of \CUASRAC]
  \label{thm:anon-cuasrac}
  If the base \CUASGen construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, then \CUASAC is an anonymous AC scheme
  according to \cite{fhs19}.
\end{theorem}

\begin{proof}
  Given \adv~ against anonymity of \CUASRAC as defined in
  \figref{fig:model-rac}, we build an adversary \advB against anonymity of
  \CUASGen as defined in \defref{def:sign-anonymity-uas}.
  %
  But, first observe that, since the revocation oracle is basically an extension
  of the \OPEN oracle -- also keeping track of the revoked users per verifier --
  queries involving challenge users are rejected if the revocation handle does
  not match for both challenge users.

  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR,ReqCredHandle$, \advB
  redirects to \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, or \OPEN (in this case,
  also keeping track of the queries, per verifier), respectively.
  Note that ``translating'' the inputs from the former into inputs for the
  latter is trivial. Also, observe that $ReqCredHandle$/\OPEN essentially
  refuses to open transcripts from challenge users (signatures, in the
  non-interactive equivalent), as $F(V,\ccidi_0) \neq F(V,\ccidi_1)$ (and,
  similarly, for $\ccidu_b$) with overwhelming probability (see the $\tyinsp
  \neq \yinsp$) check in \figref{fig:oracles2}. Obviously, if \adv~wins in its
  anonymity game, then so does \advB with the same probability.
  % 
  \qed
\end{proof}

@@

  To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
  that \adv~wins its game via the winning condition of line 9 in the RAC
  unforgeability game. The same reasoning as in \CUASAC applies here. Next, note
  that the probability of \adv~winning its game via condition $h_0 \in L$ at
  line 11 is negligible, due to soundness of the NIZK for $\NIZKRel_{\Sign}$.
  Moreover, soundness of NIZK for $\NIZKRel^{\Sign}$ as well as one-wayness
  of $F$ ensure that, if $h_1 \notin L$, then $b_1 = 1$. Namely, even when given
  $F(V,\cidi),F(V,\cidu)$ for a credential identified by $(\cidi,\cidu)$ owned
  by an honest user, and some (potentially malicious) $V$, it is not possible to
  generate $F(V',\cidi)$ nor $F(V',\cidu)$, for $V'=V$.
  % 
  \qed
\end{proof}

### 2022-08-19 prism-backend/research/gsac/app-uas-proofs.tex
Refined model for RAC. Conclusion. Complete draft (excl. app. D)

\paragraph{Unforgeability and non-frameability.} The simulation described for
the anonymity case (i.e., \advB choosing the random numbers, and concatenating
them to the message to be signed by the oracle) applies here too. Since the
interactive protocol includes non-interactive proofs for the $\NIZKRel^{\Sign}$
and $\NIZKRel^{Open}$ relations, the proofs for unforgeability and
non-frameability of \CUASGen still apply.

>>>>

\paragraph{Unforgeability and non-frameability.} The simulation described for
the anonymity case (i.e., \advB concatenating the random numbers
to the message to be signed by the oracle) applies here too. Since the
interactive protocol includes non-interactive proofs for the $\NIZKRel^{\Sign}$
and $\NIZKRel^{Open}$ relations, the proofs for unforgeability and
non-frameability of \CUASGen still apply.

### 2022-08-19 prism-backend/research/gsac/conclusion-paper.tex
Added a paragraph with real-world sample use cases. Fixed some todos.
Refined model for RAC. Conclusion. Complete draft (excl. app. D)

[1 page max]

>>>>

We present a general model for privacy-preserving signatures and authentication,
and provide a generic construction, secure in our model, that allows
different privacy-vs-utility tradeoffs to be reached.
%
Then, we prove that well-known schemes are special cases of our generic
construction. The implied schemes include group signatures, anonymous
credentials (with and without revocation), ring signatures, or the recently
proposed multimodal private signatures.

The flexibility of our model is achieved via functional placeholders that
modulate the behaviour at credential issuance time, the utility
information ``leaked'' along with the produced signatures, and the utility
information extractable from already produced signatures. These functions are
computed by the users themselves, who need to prove correct computation.
Our setting also combines features of anonymous credential schemes, like
attribute-based credentials and multiple issuers, which we extend with openers
(like in group signatures), but also enabling that multiple openers coexist.
This further increases the flexibility, by removing the tight issuer-opener
coupling in previous works.

For future work, an obvious line is to come up with (and implement) concrete
instantiations of our generic construction in order to evaluate efficiency in
real-world use cases. Also, it may be interesting to come up with alternative
generic constructions -- for instance, based on structure-preserving signatures.
%
Finally, in this work we focus only on utility over \emph{one} signature. But
extending our model and constructions to span utility over \emph{multiple}
signatures promises to be interesting, both regarding its modelling and the
potential use cases.

### 2022-08-19 prism-backend/research/gsac/relationships.tex
Refined model for RAC. Conclusion. Complete draft (excl. app. D)

We adopt the model in \cite{fhs19}, for anonymous credentials with selective
disclosure. Therein, an anonymous credential scheme is defined via $OrgKeyGen$
(which we rename to $IssKeyGen$), and $UserKeyGen$ algorithms, and $Obtain,
Issue$ and $Show,Verify$ interactive protocols. The security definitions rely on
$HU, CU, ObtIss, Obtain, Issue, Show$, and $LoR$ oracles. We refer to
\cite{fhs19} for the full details. For ease of reference, we summarize the
security definitions in \figref{fig:model-ac}.% , with inocuous
% adaptations to make them more suitable for comparison with our definitions --
% namely, we explicitly add a common setup process which is part of $IssKeyGen$
% in \cite{fhs19}.

@@

In \cite{cks10}, revocable anonymous credentials are proposed. We first give a
simple model in \figref{fig:model-rac}, extending that in
\secref{ssec:related-models-ac}. Concretely, to the functionality in
\secref{ssec:related-models-ac}, we now explicitly add the $OKeyGen$ function,
which generates the opener key pair, extend $Verify$ to receive also a list $L$
of revoked credential identifiers, and we add a function (and corresponding
oracle) $cid/\bot \gets RetrieveCredId(\osk,\utrans)$ that can extract an
identifier of the credential used in a presentation transcript \utrans. For
simplicity, we do not include the equivalent to verifiable openings, but this
would be straightforward.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.45\textwidth}
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\opk,\osk) \gets \OKeyGen(\parm) \\        
        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
        b^* \gets \adv^{\mathcal{O}_{anon}}(\parm,\ipk,\opk) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.55\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\opk,\osk) \gets \OKeyGen(\parm) \\        
        (\ipk,\isk) \gets IssKeyGen(\parm) \\
        (D,L,\st) \gets
        \adv^{\mathcal{O}_{forge}}(\parm,\ipk) \\
        \langle \cdot,(b,\utrans)\rangle
        \gets \langle \adv(\st),\Verify(\ipk,D,L)\rangle \\
        \pcif b = 0: \pcreturn 0 \\
        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j]): \pcreturn 1 \\    
        h \gets RetrieveCredHandle(\osk,\utrans) \\
        \pcif h \in L \lor h = \bot: \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for revocable anonymous credentials with selective
    disclosure based on \cite{fhs19}. 
    $\mathcal{O}_{anon} \gets \lbrace HU,CU,Obtain,Issue,ObtIss,Show,
    ReqCredHandle,LoR\rbrace$. $\mathcal{O}_{forge} \gets \lbrace HU,CU,
    Obtain,ObtIss,Issue,Show,ReqCredHandle \rbrace$. $ReqCredHandle$ is
    equivalent to \OPEN, operating on transcripts \utrans instead of signatures.
    In particular, this implies that it rejects queries for transcripts related
    to challenge users. Also, \OWNR and \ATTR tables are essentially as in
    \secref{ssec:model-uas}.}
  \label{fig:model-rac}  
\end{figure}

\subsubsection{\CUASRAC Construction.} %
Briefly, this is achieved via a $(\fissue^1,\feval^{\dattrs,F,V,L},
\finsp^{F})$-$\CUASGen^{int}$ restriction. \feval is parameterized with a PRF
$F$, a string identifying the verifier $V$ and a list $L$ of ``revocation
handles'' by $V$. Note that these can be hardcoded, though: $F$ can be common to
all verifiers, $V$ is also fixed (per verifier),
and $L$ can be updated with some reasonable frequency -- e.g., daily -- so that
the cost of recomputing $\feval^{\dattrs,F,V,L}$ is not high.
%
Since credentials in $\CUASGen^{int}$ have two identifiers (\cidi, chosen by the
issuer; and \cidu, chosen by the user), $\feval^{\dattrs,F,V,L}$ internally
computes $F(V,\cidi)$ and $F(V,\cidu)$. If either appears in $L$, \feval sets
$\yeval^0$ to $0$, which the verifier interprets as ``revoked credential''.
Otherwise, it sets $\yeval^0 \gets \lbrace \attrs_i \rbrace_{i\in\dattrs}$ and
$\yeval^1 \gets V$. $\yeval^1$ is
then used by $\finsp^F$ to compute $\yinsp \gets (F(\yeval^1,\cidi),
F(\yeval^1,\cidu))$. Thus, if the verifier $V$ wants to revoke a credential, all
it has to do is ask the opener to decrypt $\yinsp$, via $RetrieveCredHandle$.
%
In more detail, the algorithms are as follows:

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\Setup(1^\secpar)$ as in
  \CUASGen.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \KeyGen+\ISet from our
  $\CUASGen^{int}$ construction, setting $\fissue^1$ as issuance function.
\item[$(\ipk,\isk) \gets OKeyGen(\parm)$.] Runs \OKeyGen from our
  $\CUASGen^{int}$ construction, setting $\finsp^F$ as opening function.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from the
  $\CUASGen^{int}$ construction.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
  $\fissue^1$ as issuance function.
\item[$\langle 1/0,(\dattrs,\utrans)/(0,\utrans)\rangle \gets \langle Show(\ipk,
  \attrs,\dattrs,\cred),
  \Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive $\langle\Sign,\Verify\rangle$ of $\CUASGen^{int}$,
  using $\feval^{\dattrs,F,V,L}$ as signature evaluation function, and
  $\finsp^F$ as open function. The \dattrs value output by the verifier is
  the $\yeval^0$ value produced by \Sign (when accepted by \Verify).
\item[$h/\bot \gets RetrieveCredHandle(\osk,\utrans)$.]
  Gets $(\sig,\yeval^0)$ from the $\langle Show,\Verify\rangle$ transcript
  \utrans, and runs \Open from $\CUASGen^{int}$. If $\yeval^0 \neq 0$ (i.e., the
  signature was created by a non-revoked credential), this returns $(F(V,\cidi),
  F(V,\cidu))$, which the verifier can add to its revocation list $L$.
\end{description}

@@

\begin{theorem}[Anonymity of \CUASRAC]
  If the base $\CUASGen^{int}$ construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, and $F$ is one-way, then \CUASRAC is an
  anonymous AC scheme according to \cite{fhs19}.  
\end{theorem}

\begin{theorem}[Unforgeability of \CUASRAC]
  If the base $\CUASGen^{int}$ construction is unforgeable according to
  \defref{def:forge-uas}, and $F$ is one-way, then \CUASRAC is an unforgeable
  RAC scheme.
\end{theorem}

% Note that, if we aim at global credential (resp. user) revocation rather than
% verifier-local revocation, we can have \finsp just output the $(\cidi,\cidu)$
% pair (resp., \upk), and no assumption regarding $F$ is needed.

>>>>

We adopt the model in \cite{fhs19}, for anonymous credentials with selective
disclosure, which restricts to one credential per presentation. Therein, an
anonymous credential scheme is defined via $OrgKeyGen$ (which we rename to
$IssKeyGen$), and $UserKeyGen$ algorithms, and $Obtain,
Issue$ and $Show,Verify$ interactive protocols. The security definitions rely on
$HU, CU, ObtIss, Obtain, Issue, Show$, and $LoR$ oracles. We refer to
\cite{fhs19} for the full details. For ease of reference, we summarize the
security definitions in \figref{fig:model-ac}.% , with inocuous
% adaptations to make them more suitable for comparison with our definitions --
% namely, we explicitly add a common setup process which is part of $IssKeyGen$
% in \cite{fhs19}.

@@

In \cite{cks10,ckl+15}, revocable anonymous credentials are proposed. We first
give a simple model in \figref{fig:model-rac}, extending that in
\secref{ssec:related-models-ac}. Concretely, to the functionality in
\secref{ssec:related-models-ac}, we now explicitly add the $OKeyGen$ function,
which generates the opener key pair, extend $Verify$ to receive also a list $L$
of revoked credential identifiers, and we add a function (and corresponding
oracle) $cid/\bot \gets RetrieveCredId(\osk,\utrans)$ that can extract an
identifier of the credential used in a presentation transcript \utrans. For
simplicity, we do not include the equivalent to verifiable openings, but this
would be straightforward.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.43\textwidth}
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\opk,\osk) \gets \OKeyGen(\parm) \\        
        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
        b^* \gets \adv^{\mathcal{O}_{rac},LoR}(\parm,\ipk,\opk) \\
        \pcreturn b^*
      }
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.57\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\opk,\osk) \gets \OKeyGen(\parm) \\        
        (\ipk,\isk) \gets IssKeyGen(\parm) \\
        (\cid,D,L,\st) \gets
        \adv^{\mathcal{O}_{rac}}(\parm,\ipk,\opk) \\
        \langle \cdot,(b_0,\utrans_0)\rangle
        \gets \langle \adv(\st),\Verify(\ipk,D,L)\rangle \\
        \langle \cdot,(b_1,\utrans_1)\rangle
        \gets \langle Show(\ipk,\ATTR[\cid],D,\CRED[\cid]), \\
        \hspace*{7.25em}\Verify(\ipk,D,L)\rangle \\
        \pcif \OWNR[\cid] \notin \HU \lor
        D \not\subseteq \ATTR[\cid]: \pcreturn 0 \\
        \pcif b_0 = 1 \land \nexists j~\suchthat~(\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j]): \\
        \pcind \pcreturn 1 \\
        h_{\bin} \gets RetrieveCredHandle(\osk,\utrans_{\bin}) \\
        \pcif h_0 \in L \lor (h_1 \notin L \land b_1 = 0): \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for revocable anonymous credentials with selective
    disclosure based on \cite{fhs19}. 
    $\mathcal{O}_{rac} \gets \lbrace HU,CU,Obtain,Issue,ObtIss,Show,
    ReqCredHandle\rbrace$. $ReqCredHandle$ is
    equivalent to \OPEN, operating on transcripts \utrans instead of signatures
    but, in addition, keeps a list of revoked users (per verifier), based on the
    queries it receives. In $\Exp^{forge}_{\adv,rac}$, \adv~wins if it
    authenticates using a revoked credential or with insufficient attributes, or
    if it prevents an honest user from authenticating using a non-revoked
    credential.}
  \label{fig:model-rac}  
\end{figure}

\subsubsection{\CUASRAC Construction.} %
Briefly, this is achieved via a $(\fissue^1,\feval^{\dattrs,F,V,L},
\finsp^{F})$-$\CUASGen^{int}$ restriction. \feval is parameterized with a PRF
$F$, a string identifying the verifier $V$ and a list $L$ of ``revocation
handles'' by $V$. Note that these can be hardcoded, though: $F$ can be common to
all verifiers, $V$ is also fixed (per verifier),
and $L$ can be updated with some reasonable frequency -- e.g., daily -- so that
the cost of recomputing $\feval^{\dattrs,F,V,L}$ is not high.
%
Since credentials in $\CUASGen^{int}$ have two identifiers (\cidi, chosen by the
issuer; and \cidu, chosen by the user), $\feval^{\dattrs,F,V,L}$ internally
computes $F(V,\cidi)$ and $F(V,\cidu)$. If either appears in $L$, \feval aborts.
Otherwise, it sets $\yeval^0 \gets \lbrace \attrs_i \rbrace_{i\in\dattrs}$ and
$\yeval^1 \gets V$. $\yeval^1$ is
then used by $\finsp^F$ to compute $\yinsp \gets (F(\yeval^1,\cidi),
F(\yeval^1,\cidu))$. Thus, if the verifier $V$ wants to revoke a credential, all
it has to do is ask the opener to decrypt $\yinsp$, via $RetrieveCredHandle$.
%
In more detail, the algorithms are as follows:

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\Setup(1^\secpar)$ as in
  \CUASGen.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \KeyGen+\ISet from our
  $\CUASGen^{int}$ construction, setting $\fissue^1$ as issuance function.
\item[$(\ipk,\isk) \gets OKeyGen(\parm)$.] Runs \OKeyGen from our
  $\CUASGen^{int}$ construction, setting $\finsp^F$ as opening function.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from the
  $\CUASGen^{int}$ construction.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
  $\fissue^1$ as issuance function.
\item[$\langle 1/0,(\yeval,\utrans)/(0,\utrans)\rangle \gets \langle Show(\ipk,
  \attrs,\dattrs,\cred),
  \Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive $\langle\Sign,\Verify\rangle$ of $\CUASGen^{int}$,
  using $\feval^{\dattrs,F,V,L}$ as signature evaluation function, and
  $\finsp^F$ as open function. The \yeval value output by the verifier, when
  it accepts, is the $\yeval^0$ value produced by \Sign.
\item[$h/\bot \gets RetrieveCredHandle(\osk,\utrans)$.]
  Gets $(\sig,\yeval^0)$ from the $\langle Show,\Verify\rangle$ transcript
  \utrans, and runs \Open from $\CUASGen^{int}$. This returns $(F(V,\cidi),
  F(V,\cidu))$, which the verifier can add to its revocation list $L$.
\end{description}

@@

\begin{theorem}[Anonymity of \CUASRAC]
  If the base $\CUASGen^{int}$ construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, then \CUASRAC is an anonymous AC scheme
  according to \cite{fhs19}.  
\end{theorem}

\begin{theorem}[Unforgeability of \CUASRAC]
  If the base $\CUASGen^{int}$ construction is unforgeable according to
  \defref{def:forge-uas}, and $F$ is a one-way function, then \CUASRAC is an
  unforgeable RAC scheme.
\end{theorem}

Note that, if we aim at global credential (resp. user) revocation rather than
verifier-local revocation, we can have \finsp just output the $(\cidi,\cidu)$
pair (resp., \upk), and no assumption regarding $F$ is needed.
